Some figures to illustrate basic ideas in FDR

### 2016-10-19 analysis/IPvsEM.Rmd
Working on updates to IPvsEM.Rmd.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

@@

```{r generate_data}
timed_sims = function(ash.args,nsim = 20,nmin = 100,nmax = 1000,betasd = 1){
  n=10^seq(log10(nmin),log10(nmax),length=nsim)
  elapsed.time= rep(0,nsim)
  for(i in 1:nsim){
    set.seed(i)
    betahat = rnorm(n[i],sd=sqrt(1+betasd^2))
    elapsed.time[i] = system.time(do.call(ashr::ash,args = modifyList(ash.args,list(betahat = betahat, sebetahat=1))))[3]
  }
  return(data.frame(elapsed.time=elapsed.time,seed=1:nsim,n = n))
}
```

@@

```{r}
  df=data.frame()
  for(method in c("fdr","shrink")){
    for(optmethod in c("mixIP","cxxMixSquarem")){
      df = rbind(df, data.frame(method=method, optmethod=optmethod,  timed_sims(list(method=method,optmethod=optmethod),nsim=50,nmin=10,nmax=100000)))
    }
  }

```

@@

Now plot the time as a function of $n$
```{r}
  ggplot2::qplot(x=n,y=elapsed.time,data=df,col=optmethod,facets=.~method,ylab="elapsed time (s)")
```

And a zoom-in on "small" problems with $n<5000$.
```{r}
  ggplot2::qplot(x=n,y=elapsed.time,data=dplyr::filter(df,n<5000),col=optmethod,facets=.~method,ylab="elapsed time (s)")
```

>>>>

```{r chunk-options, include=FALSE}
library(REBayes)
library(ashr)
library(ggplot2)
source("chunk-options.R")
```

@@

```{r simulation_setup}
timed_sims = function(ash.args,nsim = 20,nmin = 100,nmax = 1000,betasd = 1) {
  n = 10^seq(log10(nmin),log10(nmax),length = nsim)
  elapsed.time = rep(0,nsim)
  for (i in 1:nsim) {
    set.seed(i)
    with(ash.args,cat(sprintf("%6s %13s %3d\n",method,optmethod,i)))
    betahat = rnorm(n[i],sd = sqrt(1 + betasd^2))
    elapsed.time[i] =
      system.time(do.call(ash,args = modifyList(ash.args,
        list(betahat = betahat, sebetahat = 1))))[3]
  }
  return(data.frame(elapsed.time = elapsed.time,seed = 1:nsim,n = n))
}
```

@@

```{r model_fitting}
df = data.frame()
cat("method --optmethod-- sim\n")
for(method in c("fdr","shrink")) {
  for(optmethod in c("mixIP","cxxMixSquarem")) {
    df = rbind(df,data.frame(method = method,optmethod = optmethod,
           timed_sims(list(method = method,optmethod = optmethod),
                           nsim = 50,nmin = 10,nmax = 100000)))
  }
}
cat("\n")
```

@@

Now plot time as a function of $n$:

```{r plot_results1}
qplot(x = n,y = elapsed.time,data = df,col=optmethod,facets=.~method,ylab="elapsed time (s)")
```

And a zoom-in on "small" problems with $n<5000$.

```{r plot_results2}
ggplot2::qplot(x=n,y=elapsed.time,data=dplyr::filter(df,n<5000),col=optmethod,facets=.~method,ylab="elapsed time (s)")
```

### 2016-10-19 analysis/adaptive_shrinkage.Rmd
Working on updates to IPvsEM.Rmd.

```{r chunk_options, include=FALSE}
library(ashr)
library(ggplot2)
library(scales)
source("chunk-options.R")
```

@@

cat("Summary of observed beta-hats:\n")
print(rbind(spiky     = quantile(sim.spiky$input$betahat,seq(0,1,0.1)),
            bignormal = quantile(sim.bignormal$input$betahat,seq(0,1,0.1))),
      digits = 3)

```

>>>>

```{r chunk_options, include=FALSE}
library(REBayes)
library(ashr)
library(ggplot2)
library(scales)
source("chunk-options.R")
```

@@

cat("Summary of observed beta-hats:\n")
print(rbind(spiky     = quantile(sim.spiky$input$betahat,seq(0,1,0.1)),
            bignormal = quantile(sim.bignormal$input$betahat,seq(0,1,0.1))),
      digits = 3)
```

### 2016-10-19 analysis/makefig_FDReg.Rmd
Working on updates to IPvsEM.Rmd.

1. illustrates basic idea of way q value does FDR analysis in p value space
2. compares methods in the way they decompose p values and z scores into two groups

```{r}
require(ashr)
require(qvalue)
require(locfdr)
require(mixfdr)
source("../R/plot_FDReg_hist.R") #some plotting functions
source("../R/nullalthist.R")

############################ FDReg_hist.pdf ##################################################################

#simple simulated example
ncz = 100 # number of bins in z score histograms
ntest = 10000
set.seed(111)

#simulate (with all tests alternative, true effects $\beta \sim N(0,1)$)
beta = rnorm(ntest)
sebetahat = 1
betahat = beta + rnorm(ntest, 0, sebetahat)
zscore = betahat/sebetahat
pval = pchisq(zscore^2,df=1,lower.tail=F)

#apply the different methods
res.qvalue = qvalue(pval)
res.locfdr = locfdr(zscore,nulltype=0,plot=0)
res.mixfdr = mixFdr(zscore,noiseSD=1,theonull=TRUE,plot=FALSE)
res.ash = ash(betahat,1,method="fdr")

>>>>

1. Illustrates basic idea of way q value does FDR analysis in p value space.

2. Compares methods in the way they decompose p values and z scores into
two groups.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk-options, include=FALSE}
require(ashr)
require(qvalue)
require(locfdr)
require(mixfdr)
source("chunk-options.R")
source("../R/plot_FDReg_hist.R")
source("../R/nullalthist.R")
```

## Simple simulated example

Generates DReg_hist.pdf?

```{r add_label_here}

# ncz is the number of bins in the z score histograms.
ncz   = 100
ntest = 10000
set.seed(111)

# Simulate (with all tests alternative, true effects $\beta \sim N(0,1)$).
beta      = rnorm(ntest)
sebetahat = 1
betahat   = beta + rnorm(ntest,0,sebetahat)
zscore    = betahat/sebetahat
pval      = pchisq(zscore^2,df = 1,lower.tail = FALSE)

# Apply the different methods.
res.qvalue = qvalue(pval)
res.locfdr = locfdr(zscore,nulltype = 0,plot = 0)
res.mixfdr = mixFdr(zscore,noiseSD = 1,theonull = TRUE,plot = FALSE)
res.ash    = ash(betahat,1,method = "fdr")
